---
title: "Homework 1"
author: "Mengxuan Cui"
date: "9/03/2019"
output:
  pdf_document: default
  html_document:
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment = NA)
```

## Task 1

```{r Function}
is.armstrong <- function(x) {
  result <-c()
  for(i in x){
    if(mode(i)!="numeric"){
      stop("Non numeric not allowed!")
    }else if(i%%1!=0){
      stop("Non integer not allowed!")
    }else if(i<=0){
      stop("Non positive numbers not allowed!")
    }else if(i>999){
      stop("Numbers more than 999 not allowed!")
    }else{
      a <- i %/% 100
      b <- (i-100*a) %/% 10
      c <- i %% 10
      if(a>0){
        n=3
      }else if(b>0){
        n=2
      }else{
        n=1
      }
      t = (a^n+b^n+c^n==i)
    }
    result<-append(result,t)
  }
  result
}
```


## Task 2
#### Valid inputs

```{r Valid input test}
is.armstrong(x = 1)
is.armstrong(x = 153)
is.armstrong(x = 154)
is.armstrong(x = c(153, 154))
is.armstrong(x = 1:999)
```

#### Invalid inputs

```{r Invalid input test, error=TRUE}
is.armstrong(x = -2)
is.armstrong(x = c(0,F))
is.armstrong(x = 1011)
is.armstrong(x = c(pi, 6))
is.armstrong(x = c(6, pi))
is.armstrong(x = "a")
```
## Task 3
#### Firstly, I only considered positive integers ranging from 1 to 999. I coded to check their number of digit and their condition as armstrong. I built an emepty vector and put the logicstic result into the vector one by one so that input and output had the samee length. 
#### Secondly, I thought about what the result should be if inputs were not positive integers from 1 to 999. So I added more if/else if conditions. 
#### By far I think my function is robust. One improvement I would like to make is how to detect the number of digit. Say, with aim of extension to 9999, the code has to be re-writed. 




