---
title: "Exam 2"
author: 'Mengxuan Cui'
date: "11/14/2019"
output: 
  html_document:
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment = NA, 
                      message = FALSE, warning = FALSE)
```

```{r}
library(jsonlite)
library(tidyverse)
library(httr)
library(multidplyr)
library(lubridate)
library(data.table)
library(shiny)
library(shinydashboard)
library(shinythemes)
library(dplyr)
library(readr)
```

```{r}
key <- "8089a576f2a54f8da13ccf32dbda7d51"
category_list <- c("business", "entertainment", "general", "health", "science", "sports", "technology")
source_name <- c("CNN", "Fox News", "The Wall Street Journal", "Reuters")
sortby_list <- c("relevancy","popularity","publishedAt")
```

## Task 1

1.Get all the news sources categorized as general or business, where the language is English and the country is United States. 
Filter the result to obtain the ids for CNN, Fox News, The Wall Street Journal, and Reuters.
```{r}
url1_1 <- "https://newsapi.org/v2/sources?category=business&language=en&country=us&apiKey=8089a576f2a54f8da13ccf32dbda7d51"
url1_2 <- "https://newsapi.org/v2/sources?category=general&language=en&country=us&apiKey=8089a576f2a54f8da13ccf32dbda7d51"

response1_1 <- GET(url1_1) 
response1_2 <- GET(url1_2) 

content_text1_1 <- content(response1_1, as = "text")
content_text1_2 <- content(response1_2, as = "text")

content_parsed1_1 <- fromJSON(content_text1_1)  
content_parsed1_2 <- fromJSON(content_text1_2) 

df1_1 <- content_parsed1_1$sources %>% data.frame()
df1_2 <- content_parsed1_2$sources %>% data.frame()
df1 <- rbind(df1_1,df1_2) 

df1_filtered <- df1 %>%
  filter(name %in% source_name) %>%
  select(name, id)

print(df1)
print(df1_filtered)
```

2.Get the most recent headline title from CNN, Fox News, The Wall Street Journal, and Reuters about "taxes", where the country is United States.
```{r}
url2 <- "https://newsapi.org/v2/top-headlines?country=us&q=taxes&apiKey=8089a576f2a54f8da13ccf32dbda7d51"

response2 <- GET(url2)
content_text2 <- content(response2, as = "text")
content_parsed2 <- fromJSON(content_text2) 

if(content_parsed2$totalResults == 0){
  df2 <- data.frame()
}else{
  df2 <- content_parsed2$articles %>%
    data.frame() %>%
    filter(source$name %in% source_name) %>%
    arrange(desc(publishedAt)) %>%
    select(title) %>%
    slice(1) 
}

print(df2)
```

3.Get the headline titles from CNN, Fox News, The Wall Street Journal, and Reuters on 11-01-19, where "healthcare" was in the title, the country is United States, and language is English.
```{r}
url3 <- "https://newsapi.org/v2/everything?qInTitle=healthcare&sources=cnn,fox-news,the-wall-street-journal,reuters&from=2019-11-01&to=2019-11-01&language=en&apiKey=8089a576f2a54f8da13ccf32dbda7d51"

response3 <- GET(url3)
content_text3 <- content(response3, as = "text")
content_parsed3 <- fromJSON(content_text3)

if(content_parsed3$totalResults == 0){
  df3 <- data.frame()
}else{
  df3 <-content_parsed3$articles %>% 
    data.frame() %>%
    select(title) 
}

print(df3)
```


## Task 2

1.Create get_sources() with arguments category and api_key. 
```{r}
get_sources <- function(category, api_key=key){
  
  base_url <- "https://newsapi.org/v2/sources?"
  url <- paste0(base_url,"category=",category,"&language=en&country=us&apiKey=",api_key=key)
  
  # check 'category'
  if(!is.null(category)){
    if(length(category) > 1){
      stop("No more than one category!")
    }else if(!category %in% category_list){
      stop("Category invalid!")
    }
  }

  # check 'api-key'
  if (nchar(api_key) == 0){
    stop(("Api key invalid!"))
  }
  
  # valid input 
  response <- GET(url) 
  content_text <- content(response, as = "text")
  content_parsed <- fromJSON(content_text)

  df <- content_parsed$sources %>%
    data.frame() %>%
    filter(name %in% source_name) 
  
  return(df)
 }
```

2.Create get_headlines() with arguments sources, q, page_size, page, and api_key. 

```{r}
source_id <- c("cnn", "fox-news", "the-wall-street-journal", "reuters")
```

```{r}
get_headlines <- function(sources=source_id, q='', page_size, page=1, api_key=key){
  
  base_url <- "https://newsapi.org/v2/top-headlines?country=us"
  url <- paste0(base_url,"&q=",q,"&pageSize=",page_size,"&page=",page,"&apiKey=",api_key)
  
  # check 'page_size' is num and <= 100
  if(!is.numeric(page_size)){
    stop("Page size should be a number!")
  }else if(page_size > 100){
    stop("Page size cannot not exceed 100!")
  }
  
  # check 'page'
  if(!is.numeric(page)) {
    stop("Page should be a number!")
  }
  
  # check 'api-key'
  if (nchar(api_key) == 0){
     stop(("Api key invalid!"))
  }
  
  response<- GET(url) 
  content_text <- content(response, as = "text")
  content_parsed <- fromJSON(content_text)
  
  if(is.null(content_parsed$totalResults)){
    content_parsed$totalResults <- 0
  }
  
  if(content_parsed$totalResults == 0){
    df <- data.frame()
  }else{
    df <- content_parsed$articles %>% 
      data.frame() %>%
      filter(source$id %in% sources)
  }
    
  return(df)

}
```

3.Create get_historic() with arguments q, q_title, sources, from, to, sort_by, page_size, page, api_key. 
```{r}
get_historic <- function(q='', q_title='', sources=source_id, from, to, sort_by, page_size, page=1, api_key=key){
  
  # check 'from', 'to'
  if("from">"to"){
    stop("from, to time invalid!")
  }
  
  # check sort by
  if (!(sort_by %in% c("publishedAt", "relevancy", "popularity"))) {
    stop("Sort by invalid!")
  }
  
  # check 'page_size' is number and <= 100
  if(!is.numeric(page_size)){
    stop("Page size should be  an integer!")
  }else if(page_size > 100){
    stop("Page size cannot not exceed 100!")
  }
  
  # check 'page'
  if(!is.numeric(page)) {
    stop("Page should be an integer!")
  }
  
  # check 'api-key'
  if (nchar(api_key) == 0){
     stop("Api key invalid!")
  }
 
  base_url <- "https://newsapi.org/v2/everything?"
  url <- paste0(base_url,"q=",q,"&qInTitle=",q_title,"&sources=",sources,"&from=",from,"&to=",to,"&language=en","&sortBy=",sort_by,"&pageSize=",page_size,"&page=",page,"&apiKey=",api_key)
  
  response <- GET(url)
  content_text <- content(response, as = "text")
  content_parsed <- fromJSON(content_text)

  if(is.null(content_parsed$totalResults)){
    content_parsed$totalResults <- 0
  } 
  
  if(content_parsed$totalResults == 0){
    print("No result!")
  }else{
    df <- content_parsed$articles %>% 
      data.frame() %>%
      filter(source$id %in% sources)
  }
  
  return(df)
  
}
```


## Task 3

```{r eval=FALSE}

library(shiny)
library(shinydashboard)
library(shinythemes)
library(dplyr)
library(readr)

library(shiny)
library(shinydashboard)
library(shinythemes)
library(dplyr)
library(readr)

ui <- dashboardPage(
    dashboardHeader(title = "Central News Hub"),
    
    ## Sidebar content
    dashboardSidebar(
        sidebarMenu(
            menuItem("Get Sources", tabName = "get_sources", icon = icon("search-location")),
            menuItem("Get Headlines", tabName = "get_headlines", icon = icon("heading")),
            menuItem("Get Historic", tabName = "get_historic", icon = icon("newspaper"))
        )
    ),
    
    ## Body content
    dashboardBody(
        tabItems(
            # First tab content
            tabItem(tabName = "get_sources",
                    fluidRow(
                        box(
                            width = 10,
                            title = "Parameters",
                            background = "light-blue",
                            selectInput("category1", 
                                        label = "Category",
                                        choices = c("business","entertainment", "general", "health",
                                                    "science","sports","technology"),
                                        selected = "general"
                            ),
                            textInput("key1",
                                      label = 'API-key'
                            ),
                            submitButton("search")
                        ),
                        box(
                            width = 10,
                            title = "Sources Found",
                            background = "blue",
                            tableOutput("source")
                        )
                    )
            ),
            
            # Second tab content
            tabItem(tabName = "get_headlines",
                    fluidRow(
                        box(
                            width = 10,
                            title = "Parameters",
                            background = "light-blue",
                            checkboxGroupInput("source2", 
                                            label = "Source",
                                            choices = c("cnn", "fox-news", "the-wall-street-journal", "reuters"),
                                            selected = c("cnn", "fox-news", "the-wall-street-journal", "reuters")
                            ),
                            textInput("q2", 
                                      label = "Keywords/Phrase", ""
                            )
                        ),
                        
                        box(
                            width = 5,
                            title = "Parameters",
                            sliderInput("ps2",
                                        label = "Page Size",
                                        min = 10, max = 100, value = 10
                            ),
                            sliderInput("page2",
                                        label = "Page",
                                        min = 1, max = 100, value = 1
                            )
                        ),
                            
                        box(
                            width = 5,
                            title = "Parameters",
                            textInput("key2",
                                      label = 'API-key'
                            ),
                            submitButton("search")
                        ),
                        
                        box(
                            width = 10,
                            title = "Headlines Found",
                            background = "blue",
                            tableOutput("headline")
                        )
                    )
            ),
            
            # Third tab content  sources,  
            tabItem(tabName = "get_historic",
                    fluidRow(
                        box(
                            width = 5,
                            title = "Keywords/Phrase",
                            background = "light-blue",
                            textInput("q3int", 
                                      label = "in the title only"),
                            textInput("q3", 
                                      label = "in the title and body"),
                        ),
                        
                        box(
                            width = 5,
                            title = "Sort By",
                            background = "light-blue",
                            selectInput("sortby", 
                                        label = "sort by",
                                        choices = c("relevancy","popularity", "publishedAt"),
                                        selected = "relevancy"
                            )
                        ),
                        
                        box(
                            width = 10,
                            title = "Time Range",
                            background = "light-blue",
                            dateInput("from", "From"),
                            dateInput("to", "To"),
                        ),
                        
                       
                        
                        box(
                            width = 10,
                            title = "Page Size",
                            sliderInput("ps3",
                                        label = "page size",
                                        min = 10, max = 100, value = 10
                            ),
                            sliderInput("page3",
                                        label = "page",
                                        min = 1, max = 100, value = 1
                            )
                        ),
                        
                        box(
                            width = 10,
                            title = "Parameters",
                            background = "light-blue",
                            selectInput("source3", 
                                        label = "Source",
                                        choices = c("cnn", "fox-news", "the-wall-street-journal", "reuters"),
                                        selected = " "
                            ),
                            textInput("key3",
                                      label = 'API-key'
                            ),
                            submitButton("button", "search")
                        ),
                        
                        box(
                            width = 10,
                            title = "Everything Found",
                            background = "blue",
                            tableOutput("everything")
                        )
                    )
            )
        )
    )
)


server <- function(input, output) {
    
    output$source <- renderTable({
        get_sources(input$category1, input$key1)
    })
    
    
    output$headline <- renderTable({
        get_headlines(input$source2, input$q2, input$ps2, input$page2, input$key2) %>%
            select(author, title, description, url, content)
    })
    
    
    output$everything <- renderTable({
        get_historic(input$q3, input$q3int, input$source3, input$from, input$to, input$sortby, input$ps3, input$page3, input$key3) %>%
            select(author,title,description,url,content)
    })
    
}

shinyApp(ui, server)


```




